---
title: "PSTAT 131 HW2"
author: "Jiacong Wu"
date: "2022-10-17"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidymodels)
library(tidyverse)
f = "abalone.csv"
```


```{r}
aba_data = read.csv(file = f)
head(aba_data)
```
Question 1

```{r}
aba_data$age <-aba_data$rings + 1.5
head(aba_data)
```

```{r}
aba_data%>%
  ggplot(aes(x = age)) + 
  geom_histogram()
```

The distribution of age is left skewed, much of the mass of its distribution is at the lower end, majority of the abalones are aged less than 15.

Question 2

```{r}
set.seed(1000)

aba_split <- initial_split(aba_data, prop = 0.75,
                                strata = age)
aba_train <- training(aba_split)
aba_test <- testing(aba_split)
```

Question 3

Rings should not be included because the age is diredctly calculated from rings. There is a super strong correlation between the two variables. If rings is included in the predictors, the model will be overfit. 

```{r}
aba_recipe <-
  recipe(age ~ type + longest_shell + diameter + height + whole_weight + shucked_weight + viscera_weight + shell_weight, data = aba_train)%>%
  step_dummy(all_nominal_predictors())%>%
  step_interact(terms = ~ starts_with('type'):shucked_weight)%>%
  step_interact(terms = ~ longest_shell:diameter)%>%
  step_interact(terms = ~ shucked_weight:shell_weight)%>%
  step_center(all_predictors())%>%
  step_scale(all_predictors())
aba_recipe
```

Question 4

```{r}
lm_model <- linear_reg() %>% 
  set_engine("lm")
```

Question 5

```{r}
aba_lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(aba_recipe)
```

Question 6

```{r}
lm_fit <- fit(aba_lm_wflow, aba_train)
lm_fit
```

```{r}
predict(lm_fit, data.frame(type = "F",longest_shell = 0.50,diameter = 0.10, height = 0.30, whole_weight = 4, shucked_weight = 1, viscera_weight = 2, shell_weight = 1))
```
Question 7

```{r}
library(yardstick)
aba_metric = metric_set(rsq,rmse,mae)
aba_train_result = predict(lm_fit,aba_train %>% select(-age,-rings))
aba_train_result =bind_cols(aba_train_result,aba_train %>% select(age))
head(aba_train_result)
```

```{r}
aba_metrics = aba_metric(aba_train_result,truth =age, estimate = .pred)
aba_metrics
```











